\eabstract{
    This thesis studies the problem of generating UI component code from natural language descriptions and presents the design and implementation of a Web-based generation system. The system targets Vue 3 Single File Components. After users provide a component name, requirement description, and constraint information, the system invokes a large language model to generate component code and further supports online preview, history review, and file download. The focus of this work is not limited to one-time code generation, but to building an executable, traceable, and controllable engineering workflow.

The system adopts a front-end/back-end separated B/S architecture. The frontend is responsible for requirement input, streaming result display, code presentation, and runtime preview. The backend is responsible for authentication, project space management, task creation, model invocation, structured result extraction, version persistence, and security control. To improve output usability under unstable model responses, the generation pipeline introduces format constraints, structured extraction, and fallback completion for missing sections. To reduce runtime risks, a dual-layer safety mechanism is designed by combining server-side rule scanning with client-side preview interception. In addition, task-level mutual exclusion, rate limiting, unified exception handling, and request logging are applied to improve operational stability.

The thesis further completes requirement analysis, overall design, database design, core function implementation, and functional, performance, and security testing. The test results show that the system can stably complete the main workflow of task creation, streaming generation, online preview, version management, and result download, while also providing explicit handling for unauthorized access, rate-limit triggers, and unsafe generated code. The study demonstrates that natural-language-driven UI component generation is engineering-feasible for course projects and small to medium front-end development scenarios, and it provides a foundation for future extensions such as iterative generation, automatic evaluation, and multi-model integration.
}{Natural Language Description, UI Component Generation, Vue 3, Streaming Generation, System Implementation}
